In fact, the writing of papers is unavoidable in all subjects. In addition to a
well-founded content, a clearly arranged text also contributes significantly to
the comprehensibility of the work. This template was developed in order to
reduce the hurdles for the use of the text typesetting system \LaTeX\ for
writing student papers. Due to the large number of different specifications
this template should rather be understood as a construction kit and a
collection of examples and not be understood to be a layout guideline. Own
commands are only defined in those places where it is unavoidable (e.g. in the
design of the cover pages etc.). This makes it easy even for the advanced
\LaTeX user to add his own adaptations to this template.

Chapter~\ref{sec:tpl} deals with the structure and functioning of this template.
In addition, it explains how the template can be set up for the respective
purpose. This chapter should therefore not be skipped, as it will help you to
quickly find your way around the basic template.

General notes on writing papers are covered in chapter~\ref{sec:content}. In
addition, the chapter contains advice on how \LaTeX\ supports you in
implementing the formal aspects of a thesis.

Chapter~\ref{sec:final} summarises important notes on the final check. The
effort required to check that the spelling is correct should not be
underestimated. Allow at least two weeks buffer. Particularly in the case of
more extensive (bachelor's thesis or diploma thesis and upwards) are printed in
a print shop. There are a few pitfalls to be aware of to ensure a smooth
process. Here, too, you can make do with a small additional time buffer of half
a week to a week for the final check of the work. This can avoid a lot of
stress. So skip this chapter \textbf{not} when it comes to the big picture.

In Appendix~\ref{app:latex} a collection of \LaTeX examples for different use
cases is provided. The corresponding subsections are largely independent of
each other and should only be read as needed.

We hope to have saved you some work with this template and wish you good luck!
We wish you good luck!
